---
title: "Untitled"
---

Install purrr 1.0.0 with:

```r
pak::pak("cran/purrr@1.0.0")
```

## Breaking changes

There are four important changes that you should be aware of:

* `pluck()` behaves differently when extracting 0-length vectors.
* The `map()` family uses the tidyverse rules for coercion and recycling.
* All functions that modify lists handle `NULL` consistently.
* We've deprecated functions that aren't related to the core purpose of purrr.

### pluck() and zero-length vectors

```{r}
library(purrr)

x <- list(y = list(a = character(), b = NULL))
x
```

```{r}
x %>% pluck("y", "a", .default = NA)
```

```{r}
x |> pluck("y", "b", .default = NA)
```

```{r}
x |> pluck("y", "c", .default = NA)
```

This also impacts `map_*`:

```{r}
x <- list(list(1), list(), list(NULL), list(character()))
x

x %>% map(1, .default = 0) %>% str()
```

purrr has a number of functions that modify a list: pluck<-(), assign_in(), modify(), modify2(), modify_if(), modify_at(), and list_modify(). Previously, these functions had inconsistent behaviour when you attempted to modify an element with NULL: some functions would delete that element, and some would set it to NULL

```{r}
x1 <- x2 <- x3 <- list(a = 1, b = 2)

x1$a <- NULL
str(x1)
#> List of 1
#>  $ b: num 2

x2["a"] <- list(NULL)
str(x2)
#> List of 2
#>  $ a: NULL
#>  $ b: num 2

```

Now functions that edit a list will create an element containing NULL:

x3 |> 
  list_modify(a = NULL) |> 
  str()
#> List of 2
#>  $ a: NULL
#>  $ b: num 2

x3 |> 
  modify_at("b", \(x) NULL) |> 
  str()
#> List of 2
#>  $ a: num 1
#>  $ b: NULL


x3 |> 
  list_modify(a = zap()) |> 
  str()
#> List of 1
#>  $ b: num 2
```

### Deprecations



cross() and all its variants have been deprecated because they’re slow and buggy, and a better approach already exists in tidyr::expand_grid().
